---
title: "`SimpLin` package demonstration"
author: "Liz Lawler"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SimpLin-package-demonstration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

With this package, you can perform a simple linear regression analysis. This package provides one function, `SimpLinR` which takes two arguments:
- `x`: a numeric vector of length $n$, the predictor variable
- `y`: a numeric vector of length $n$, the response variable

The function automatically adds a column of ones to the `x` vector to create a design matrix $\bf{X}_{n, 2}$. The function finds the least squares estimate (LSE) of your coefficients through the following matrix multiplication: 
$$(\bf{X}^T\bf{X})^{-1}\bf{X}^T\bf{y}$$
The function also calculates the standard errors of the parameter coefficients following similar linear model theory, along with calculating the residuals and predicted values. Below is a brief example with corresponding output.

```{r setup}
library(SimpLin)

x <- c(1,5,6)
y <- c(1,2,3)
fit <- SimpLinR(x, y)
```

Estimated coefficients, with intercept always first
```{r}
fit$coefs
```

Standard errors of both coefficients
```{r}
fit$std_errors
```

95% confidence interval for both coefficients; 2.5% is the first column and 97.5% is the second column
```{r}
fit$conf_int
```

Predicted values
```{r}
fit$preds
```

And finally, the residuals
```{r}
fit$resids
```
